---
title: "Behavioral, information and monetary interventions to reduce energy consumption in households: A “living” systematic review"
author: "diana danilenko"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, 
                      results="hide",
                      error = F,
                      warning = F,
                      message = F)
```

```{r libraries}
library(metafor) 
library(meta)
library(metadat)
library(dplyr)
library(ggplot2)
library(texreg)
library(tidyverse) 
library(summarytools)
library(htmltools)
library(rmarkdown)
library(devtools)
library(clubSandwich)
library(cowplot)
library(ggrepel) 
library(igraph)
library(nmarank)
library(knitr)
library(kableExtra)
library(gemtc)
library(rjags)
library(gridExtra)
library(modelsummary)
library(readr)
library(boot)
library(haven)
library(stringr)
library(shiny)
library(readxl)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
```

```{r functions}
source("functions_v1.R")
source("functions_nma.R")
```

```{r data}
load("lsr_data_2025-20250513.R")
# save data in R database before outlier exlusion
# save(dfinc,file="lsr_data_2024-11042025.R")
```

```{r process}
# ANALYSIS USING 6 MAIN CATEGORIES MAPPING - FEEDBACK, INFORMATION, SOCIAL, MOTIVATION, MONETARY, DYNAMICPRICING

# Prepare data for analysis
dfinc_all <- dfinc %>%
  mutate(
    Feedback = ifelse(`Historical` == 1  | `Home Energy Report` == 1 | `In home display` == 1 | `Smart Metering` == 1, 1, 0),
    Information = ifelse(`Awareness Campaign` == 1 | `Bills` == 1 |`Home audits` == 1 | `tips` == 1, 1, 0),
    SocialComparison = ifelse(`Injunctive Norm / Social Norm` == 1 | `peer comparison` == 1, 1, 0),
    Motivation = ifelse(`Commitment strategies` == 1 | `Competition` == 1 | `Gamification` == 1 | `Goal Setting` == 1 | `Moral suasion` == 1, 1, 0),
    DynamicPricing = ifelse(`Critical Peak Pricing` == 1 | `Dynamic Pricing` == 1 | `Peak Load Pricing` == 1 | `Real-time Pricing` == 1 | `ToU` == 1,  1, 0),
    MonetaryRewards = ifelse(`Rewards` == 1, 1, 0)
  ) %>% 
  replace_na(list(
    Feedback = 0,
    Information = 0,
    SocialComparison = 0,
    Motivation = 0,
    MonetaryRewards = 0,
    DynamicPricing = 0
  )) %>%
  mutate(Feedback_2 = ifelse(Feedback == 1, "Feedback1", "Feedback0")) %>% 
  mutate(Information_2 = ifelse(Information == 1, "Information1", "Information0")) %>% 
  mutate(SocialComparison_2 = ifelse(SocialComparison == 1, "SocialComparison1", "SocialComparison0")) %>% 
  mutate(Motivation_2 = ifelse(Motivation == 1, "Motivation1", "Motivation0")) %>% 
  mutate(MonetaryRewards_2 = ifelse(MonetaryRewards == 1, "MonetaryRewards1", "MonetaryRewards0")) %>%
  mutate(DynamicPricing_2 = ifelse(DynamicPricing == 1, "DynamicPricing1", "DynamicPricing0")) %>%
  mutate(Treatment1 = paste(Feedback_2, Information_2, SocialComparison_2, Motivation_2, MonetaryRewards_2, DynamicPricing_2, sep = ":")) %>%
  filter(Treatment1 != "Feedback0:Information0:SocialComparison0:Motivation0:MonetaryRewards0:DynamicPricing0") %>% # Exclude effect size that doesn't get mapped to a valid intervention
  mutate(treatment = mapping_vector[Treatment1])

dfinc_all <- dfinc_all %>%
  mutate(intervention = apply(select(., Feedback, Information, SocialComparison, Motivation, MonetaryRewards, DynamicPricing), 1, function(row) {
    cols <- names(row)[which(row == 1)]   # get names of columns where the value is 1
    if(length(cols) > 0) {
      paste(cols, collapse = "_")         # concatenate with underscore
    } else {
      NA                                  # if no values are 1, set to NA
    }
  }))

dfinc_all$InterventionID <- 1:nrow(dfinc_all)

dfinc_all$Feedback <- factor(dfinc_all$Feedback)
dfinc_all$Information <- factor(dfinc_all$Information)
dfinc_all$SocialComparison <- factor(dfinc_all$SocialComparison)
dfinc_all$Motivation <- factor(dfinc_all$Motivation)
dfinc_all$MonetaryRewards <- factor(dfinc_all$MonetaryRewards)
dfinc_all$DynamicPricing <- factor(dfinc_all$DynamicPricing)
```

Our living systematic review and meta-analysis continuously integrate available evidence to answer the following questions:

1. To what extent can information, behavioral and monetary interventions reduce energy consumption of households in residential buildings?
2. What is the relative effectiveness of interventions?
3. How effective are combinations of different interventions?

Below you can find an overview of the data from studies up to January 2025.

```{r population}
population <- dfinc %>%
  distinct(Authors, `document PY`, `document title`, .keep_all = TRUE) %>%
  summarise(total = sum(total_sample_size, na.rm = TRUE))
population <- population$total[[1]]
```

There are `r nrow(dfinc)` effect sizes from `r nrow(unique(dfinc[, c("Authors", "document PY", "document title")]))` studies, covering a population of `r format(population, scientific = FALSE)` in `r nrow(unique(na.omit(dfinc$country)))` countries.

### Histogram of yearly publications of included studies
```{r hist, results='markup'}
df_unique <- dfinc %>%
  distinct(Authors, `document PY`, `document title`)

# count number of documents per year
docs_per_year <- df_unique %>%
  count(`document PY`, name = "n")

# plot histogram
ggplot(docs_per_year, aes(x = `document PY`, y = n)) +
  geom_col(fill = "darkslategrey") +
  labs(
    title = "Number of included documents per year"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Map of included studies
```{r map, results='markup'}
world_map <- ne_countries(scale = "medium", returnclass = "sf")

dfinc <- dfinc %>%
  mutate(country = case_when(
    country == "USA" ~ "United States of America",
    country == "UK" ~ "United Kingdom",
    country == "Korea" ~ "South Korea",
    TRUE ~ country  
  ))

countries <- unique(na.omit(dfinc$country))

#world_map$in_sample <- ifelse(world_map$name %in% countries, "yes", "no")

# ggplot(data = world_map) +
#   geom_sf(aes(fill = in_sample), color = "black", size = 0.5) +  
#   scale_fill_manual(values = c("yes" = "lightblue", "no" = "white")) +  
#   theme_minimal() +
#   labs(title = "Map of included studies",
#        subtitle = paste("Number of countries:", length(countries))) +
#   theme(plot.title = element_text(hjust = 0.5),
#         plot.subtitle = element_text(hjust = 0.5))

df_uniquec <- dfinc %>%
  distinct(Authors, `document PY`, `document title`,`country`) %>%
  filter(! is.na(country))

country_counts <- df_uniquec %>%
  group_by(country) %>%
  summarise(study_count = n(), .groups = "drop")

world_map_n <- world_map %>%
  left_join(country_counts, by = c("name" = "country"))

ggplot(data = world_map_n) +
  geom_sf(aes(fill = study_count), color = "black", size = 0.5) + 
  scale_fill_gradient(low = "honeydew", high = "darkslategray", na.value = "white") +
  theme_minimal() +
  labs(title = "Number of studies per country") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

```{r summary}
# factor variables
sumVarsFactor <- c(#"intervention",
                   "Opt_in_out",
                   "StatsMethod",
                   "StudyDesign",
                   "Randomisation",
                   "Region",
                   "Weather",
                   "cat_criterion1",
                   "cat_criterion2",
                   "cat_criterion5",
                   "cat_criterion6",
                   "cat_criterion7")

# numeric variables
sumvarsNum <- c("smd",
                "var_smd")

dfinc_all[sumVarsFactor] <- lapply(dfinc_all[sumVarsFactor], factor)
dfinc_all[sumvarsNum] <- lapply(dfinc_all[sumvarsNum], as.numeric)

# for(col in names(select(dfinc_all,all_of(sumVarsFactor)))) {
#   freq_table <- freq(dfinc_all[[col]], style = "rmarkdown", cumul=FALSE, report.nas = FALSE, totals = FALSE)
#   print(freq_table)
# }

# dfinc_all %>%
#   select(all_of(c(sumVarsFactor,sumvarsNum))) %>% 
#   dfSummary(graph.col = T, style = "grid", na.col = F, 
#             valid.col = F, varnumbers = F, class = F, 
#             plain.ascii = T, view = F) %>%
#   print(file = paste0("summarystatistics", format(Sys.Date(), "%d%m%Y"), ".html"))

# knitr::include_url(paste0("summarystatistics", format(Sys.Date(), "%d%m%Y"), ".html"), height = "800px")
```

### Summary statistics: 

<iframe src="summarystatistics13052025.html" width="100%" height="800px" style="border:none;"></iframe>

And an overview of included effect sizes per intervention:
```{r interventions, results = 'markup'}
# use this for showing n observations per intervention
int_count <- table(dfinc_all$intervention)
int_df <- as.data.frame(int_count)
int_df_sorted <- int_df[order(-int_df$Freq), ]
rownames(int_df_sorted) <- NULL 

library(kableExtra)
kable(int_df_sorted, col.names = c("Intervention", "Count")) %>%
  kable_styling(bootstrap_options = c("striped", "hover","condensed"), font_size = 9,full_width = F) 
```

```{r meta-analysis, results = 'markup'}

dfinc_all$se = (dfinc_all$var_smd)^(1/2)
# dfinc_all <- dfinc_all %>%
#  filter (intervention %in% c("Feedback","Information","SocialComparison","Motivation","MonetaryRewards", "DynamicPricing"))

meta_all <- rma.mv(smd, var_smd, random = ~ as.factor(effectID) | as.factor(documentID),
                   data = dfinc_all, method = "REML")
#summary(meta_all)

meta_all_se <- rma.mv(smd, var_smd, mods = ~ se,
                      random = ~ as.factor(effectID) | as.factor(documentID), data = dfinc_all, method = "REML")
#summary(meta_all_se)

meta_all_smd <- rma.mv(smd, var_smd, mods = ~ var_smd,
                      random = ~ as.factor(effectID) | as.factor(documentID), data = dfinc_all, method = "REML")
#summary(meta_all_smd)

# meta_model<-rma.mv(smd, var_smd, mods =  ~ Feedback:Information:SocialComparison:Motivation:MonetaryRewards:DynamicPricing+0,
#                    random = ~ as.factor(effectID) | as.factor(documentID), data = dfinc_all, method = "REML")
#summary(meta_model)
```

Average effect size: `r round(meta_all[['beta']], 2)`

Average effect size adjusted for small study or publication bias (based on variance): `r round(meta_all_smd[['beta']], 2)`

Best performing intervention:

Correction for risk of bias: 

[Study protocol](https://onlinelibrary.wiley.com/doi/10.1002/cl2.1424)

If you know of a study that should be included in this systematic review & meta-analysis, especially from under-represented regions, please reach out to us at [e-mail](mailto:dianada@pik-potsdam.de).
